SVA-DEA benchmark

### 2020-05-12 main_figures/dimensionality.Rmd
updated color mapping

p3 <- renameHrows(
  evalHeatmap( res, what=c("NMI","min_pr"), agg.by=c("norm","dims"), 
                   row_split=gsub("norm\\.","",norm), reorder_rows=TRUE, anno_legend=FALSE) + 
  evalHeatmap(res, what=c("ARI"), agg.by=c("norm","dims"), row_split=gsub("norm\\.","",norm), 
              reorder_rows=TRUE, filterExpr=n_clus==true.nbClusts, 
              anno_legend=FALSE, title="ARI at\ntrue k"),
  rnfn
)
p3 <- grid.grabExpr(draw(p3))
```

>>>>

p3 <- renameHrows(
  evalHeatmap( res, what=c("NMI","min_pr"), agg.by=c("norm","dims"), 
                   row_split=gsub("norm\\.","",norm), reorder_rows=TRUE, anno_legend=FALSE) + 
  evalHeatmap(res, what=c("ARI"), agg.by=c("norm","dims"), row_split=gsub("norm\\.","",norm), 
              reorder_rows=TRUE, filterExpr=n_clus==true.nbClusts, 
              anno_legend=FALSE, title="ARI at\ntrue k"),
  rnfn
)
p3 <- grid.grabExpr(draw(p3, annotation_legend_list=.scaledLegend(), merge_legend=TRUE, heatmap_legend_side="bottom"))
```

### 2020-05-12 main_figures/filtering.Rmd
updated color mapping

```{r}
suppressPackageStartupMessages({
  library(ComplexHeatmap)
  library(circlize)
  library(ggplot2)
  library(ggridges)
  library(cowplot)
  library(SingleCellExperiment)
  library(pipeComp)
})
theme_set(theme_cowplot(font_size = 12))
source("../misc_functions.R")
```

@@

```{r figure2, fig.width=8, fig.height=8.5}
res <- readRDS("../data/results_filtering.rds")
m <- scrna_evalPlot_filtering(res, returnTable=TRUE)
m$doubletRemoval <- !grepl("doubletmethod=none;", m$method)
m$filter <- factor(sapply(strsplit(as.character(m$method),"\\.|="), FUN=function(x) rev(x)[1]),
                     c("nofilter","lenient","default","pca","pca2","stringent","veryStringent"))
cols <- c("black", pipeComp::getQualitativePalette(length(levels(m$filter))-1))
names(cols) <- levels(m$filter)

# ggplot(m, aes(maxPCout, meanF1, group=method, colour=filter, shape=doubletRemoval)) + geom_point(size=3) + facet_wrap(~dataset, scales="free") + scale_color_manual(values=cols) + xlab("Max proportion of subpopulation excluded")

p2 <- ggplot(m, aes(maxPCout, F1atK, group=method, colour=filter, shape=doubletRemoval)) + geom_point(size=3) +
  # geom_line(aes(group=doubletRemoval), colour="lightgrey") + 
  facet_wrap(~dataset, scales="free") + scale_color_manual(values=cols) + 
  xlab("Maximum proportion of cells excluded per subpopulation") + ylab("mean F1 at true number of clusters")

>>>>

```{r}
suppressPackageStartupMessages({
  library(ComplexHeatmap)
  library(circlize)
  library(ggplot2)
  library(ggridges)
  library(cowplot)
  library(SingleCellExperiment)
  #library(pipeComp)
})
devtools::load_all("../../pipeComp/")
theme_set(theme_cowplot(font_size = 12))
source("../misc_functions.R")
```

@@

```{r figure2, fig.width=8, fig.height=8.5}
res <- readRDS("../data/results_filtering.rds")

p2 <- scrna_evalPlot_filtering(res, atNearestK=TRUE, alpha=0.8) + 
  ylab("Mean F1 at best number of clusters")

### 2020-05-12 main_figures/normalization.Rmd
updated color mapping

lgd <- Legend(col_fun=colorRamp2(1:100, viridisLite::inferno(100)), at=c(1,50,100), 
              title="MADs", labels=c("worst","median","best"), direction="horizontal")
p3 <- grid.grabExpr(draw(
  renameNorm(evalHeatmap(res, step="clustering", what=c("MI","ARI"), agg.by = "norm", 
              reorder_rows=TRUE, anno_legend=FALSE, row_split=classifyNorms(norm), row_title="Clustering accuracy") + 
    evalHeatmap(res, step="clustering", what="ARI", agg.by = "norm", 
                filter=n_clus==true.nbClusts, reorder_rows=TRUE, anno_legend=FALSE,
                row_split=classifyNorms(norm), name="ARI at true k", title="ARI at true k")),
  heatmap_legend_side = "bottom", merge_legend=TRUE, annotation_legend_list=lgd))
```

>>>>

lgd <- Legend(col_fun=colorRamp2(1:100, viridisLite::inferno(100)), at=c(1,50,100), 
              title="MADs", labels=c("worst","median","best"), direction="horizontal")
p3 <- grid.grabExpr(draw(
  renameNorm(evalHeatmap(res, step="clustering", what=c("MI","ARI"), agg.by = "norm", 
              reorder_rows=TRUE, anno_legend=FALSE, row_split=classifyNorms(norm), row_title="Clustering accuracy") + 
    evalHeatmap(res, step="clustering", what="ARI", agg.by = "norm", 
                filter=n_clus==true.nbClusts, reorder_rows=TRUE, anno_legend=FALSE,
                row_split=classifyNorms(norm), name="ARI at true k", title="ARI at true k")),
  heatmap_legend_side = "bottom", merge_legend=TRUE, annotation_legend_list=.scaledLegend()))
```

### 2020-05-12 main_figures/svadea.Rmd
updated color mapping

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(pipeComp)
  library(grid)
  library(ComplexHeatmap)
  library(circlize)
})
theme_set(theme_cowplot(font_size = 11))
res1 <- res <- readRDS("../svadea/results/aggregated.rds")
res1$evaluation$dea <- lapply(res1$evaluation$dea, FUN=function(x){
  x[which(x$k==1),]
})
```

@@

hts <- dea_evalPlot_sig(res, what=c("logFC.pearson","TPR"), agg.by=c("sva.method","k"), row_split="sva.method", 
                     anno_legend=FALSE, show_column_names=TRUE, font_factor=0.85, scale="colCenterScale") +
  dea_evalPlot_sig(res, what="FDR", agg.by=c("sva.method","k"), row_split="sva.method", 
                     anno_legend=FALSE, show_column_names=TRUE, font_factor=0.85, scale="colCenterScale",
                     col=rev(viridisLite::inferno(100)), value_cols=c("white","black"))
lgd <- Legend(col_fun=colorRamp2(1:100, viridisLite::inferno(100)), at=c(1,100), 
              title="MADs", labels=c("worst","best"), direction="horizontal")
hts <- pipeComp:::.renameHrows(hts, f = function(x) gsub("none > 1", "none",x, fixed=TRUE))
#draw(hts, heatmap_legend_side = "bottom", merge_legend=TRUE, annotation_legend_list=lgd)

p <- plot_grid(
  plot_grid(
    dea_evalPlot_curve(res1, agg.by=c("sva.method","dea.method"), colourBy="dea.method", shapeBy="sva.method") + ggtitle("Using a single surrogate variable"),
    dea_evalPlot_curve(res, agg.by=c("sva.method","k"), colourBy="k", shapeBy="sva.method") + ggtitle("Increasing the number of surrogate variables"),
    nrow=2, labels=LETTERS[1:2]
  ),
  grid.grabExpr(draw( hts, heatmap_legend_side = "bottom", merge_legend=TRUE, 
                      annotation_legend_list=lgd)),
  nrow=1, rel_widths=c(5,2.2), labels=c(NA,"C")
)
pdf("svadea.pdf", width=11.5, height=6.8)
p
dev.off()
p
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(pipeComp)
  library(grid)
  library(ComplexHeatmap)
  library(circlize)
})
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 11))
res1 <- res <- readRDS("../svadea/results/aggregated.rds")
res1$evaluation$dea <- lapply(res1$evaluation$dea, FUN=function(x){
  x[which(x$k==1),]
})
```

@@

hts <- evalHeatmap( res, step="dea", what="logFC.pearson", agg.by=c("sva.method","k"), 
                    row_split="sva.method", anno_legend=FALSE, show_column_names=TRUE, 
                    font_factor=0.85, scale="colCenterScale" ) +
  evalHeatmap( res, step="dea", what="TPR", agg.by=c("sva.method","k"), 
                    row_split="sva.method", anno_legend=FALSE, show_column_names=TRUE, 
                    font_factor=0.85, scale="colCenterScale", filterExpr=threshold==0.05 ) +
  evalHeatmap(res, step="dea", what="FDR", agg.by=c("sva.method","k"), row_split="sva.method", 
                     anno_legend=FALSE, show_column_names=TRUE, font_factor=0.85, scale="colCenterScale",
                     col=rev(viridisLite::inferno(100)), value_cols=c("white","black"), filterExpr=threshold==0.05)
hts <- pipeComp:::.renameHrows(hts, f = function(x) gsub("none > 1", "none",x, fixed=TRUE))
#draw(hts, heatmap_legend_side = "bottom", merge_legend=TRUE, annotation_legend_list=.scaledLegend())

p <- plot_grid(
  plot_grid(
    dea_evalPlot_curve(res1, agg.by=c("sva.method","dea.method"), colourBy="dea.method", shapeBy="sva.method") + ggtitle("Using a single surrogate variable"),
    dea_evalPlot_curve(res, agg.by=c("sva.method","k"), colourBy="k", shapeBy="sva.method") + ggtitle("Increasing the number of surrogate variables"),
    nrow=2, labels=LETTERS[1:2]
  ),
  grid.grabExpr(draw( hts, heatmap_legend_side = "bottom", merge_legend=TRUE, 
                      annotation_legend_list=.scaledLegend())),
  nrow=1, rel_widths=c(5,2.2), labels=c(NA,"C")
)
pdf("svadea.pdf", width=11.5, height=6.8)
p
dev.off()
p
```
